Ambrose walked out to the yard with his backpack heavy and his shoulders hunched.
Leaving school, as well as entering school, or just being at school, was always an annoyance.
He was a senior, but instead of respect that title just gave him a sense of detachment, now that there were younger kids to make fun of him on the hallways.
-- Hello there, Rosie -- called a girl with long blond hair -- your boyfriend wanted to know weather you're still sore from yesterday -- she said.
'Brose walked faster and tried not to make eye contact, even though he knew that never worked.
-- Come on, Rosie, I know you heard me -- she insisted -- If you want I can braid your hair for your next date.
-- Are you jealous? -- he snapped -- Are you afraid he's gonna like me better than he liked you, is that it? Afraid he's gonna tell you "oh Bea, the truth is, you suck at sucking dick. 
Even with all the practice you had!"
-- You're such a fag, Rosie! -- she replyed, venomously. He rushed away.
The yard was full of kids, and he hated all of them. He looked around but he couldn't see neither of his friends. Then his eyes picked up someone he recognized, standing right at the gates.
Now this, he thought. He hated seeing her here after school, specially when there were bullies around (which is to say, always). She stood upright with her small, lean body as if
she could stand for ever. Her skin was tanned brown and her eletric blue hair shone against it, and against the new hair, dark brown, that was growing on the shaved side of her head.
His fists clenched up a bit as he looked around, checking if anyone had seen him staring at her. Maybe he could just pretend he hadn't seen her, 
and kill some time reading a book or something until she went away. He opened his bag and took out a notebook and a pen. Maybe he could draw a little.
-- Now what's that, Rosie? -- asked a boy a year younger than him, pulling the notebook away. -- Is this were you keep sketches of all the boys you're in love with?
-- Aw, give it back -- Ambrose cried, glancing at her rapidly. This was bad.
-- Hey, guys, Rosie fancies herself an artist!
The notebook was filled with drawings of monsters and warriors, of course, with the occasional magical girl.
-- Is this your boyfriend? -- asked the bully, pointing at a drawing of Ambrose's latest game character, a dashing caped swordsman named Sterek Wolfpaw.
-- No, you can have him -- said Brose, annoyed. He didn't mean it, though. Wolfpaw was too good for this brat.
-- Or maybe this one is? -- the boy pointed at another drawing -- Or girlfriend maybe? I really can't tell, what's this supposed to be, a fairy?
Ambrose's eyes went wide.
-- Just give it back. -- he asked again.
-- Hey -- said another boy -- Isn't that the chick at the gate?
-- Oooh yeah, -- said the bully. -- Blue hair, skinny, looks like a dude, that's her. Hey, bluenette!
The girl by the gate looked at them, while Ambrose tried to hide behind them. It failed.
-- Ooooh Rosie, how are you! -- yelled the girl, coming over.
Ambrose sighed and straightened up to waive at her.
-- Hello, Dani.
Her name was Danielle. She went to a different school, but every other day she came to his school and waited for the classes to end.
-- What are those dudes calling me this time? -- she asked, smiling. He didn't like the smile. It looked dangerous on her face.
-- A dude -- said Brose.
-- Shut up, Rosie -- said the bully -- We can see now that this is not a dude indeed. You're womanly enough for me!
Dani seemed intent on ignoring the boy.
-- No, I mean the other thing. Bluenette?
-- Something they picked up from reading too much furry porn probably -- he said, rapidly. This was untrue. They had picked up the term from him,
when they had overheard a discussion between him and his two friends about... fanfiction.
-- Well I like it -- said Dani, smiling at the boys. They were a little flustered by her smile, probably because she was so beautiful up close. -- Now you little cunts can go bother some
other girl, okay?
The boys blinked.
-- What?!
-- Wait, give me back the notebook! -- said Ambrose, but they didn't even acknowledge that, as they processed what Dani had said.
-- Hey, listen, bitch, just because you look like a suicide girl doesn't mean we're gonna be your litle boytoys -- one of them said.
-- Of course it does! -- said Dani, -- and if it doesn't, maybe I have to train you a little better.
She moved fast and grabbed his nose, and pressed it so hard he bend over trying to free himself. With the other hand she took Brose's notebook, and then it was all over very fast.
-- Crazy bitch! -- the boy yelled, still bent over and red-nosed.
-- Yeah whatever -- said Dani. -- Let's go, Rosie.
She dragged him by the wrist, towards the gate. Ambrose looked around and saw every eye on the yard on them. School would be even more hellish tomorrow, to be sure.
-- Let go! -- yelled Brose, pulling back.
-- Yeesh, you don't have to yell! I just wanted to get us away from those idiots.
-- Look, Danielle, I'm not gonna say I wasn't happy to see you shut up Simon...
-- Who's Simon? -- she asked, interrupting him.
-- The guy you just almost ripped the nose off of? And I'm glad you did, really, but...
-- Hm? -- she looked away, as if she weren't listening at all. He took a deep breath.
-- But I really don't like you, you're stuck up and annoying and you don't respect me at all and you just expect everyone around you to bow to you or something 
and you hanging out with me is just gonna draw more bullying anyway, so, like, could you just not?
She turned his eyes to him. They were deep brown and kinda breathtaking. This just made her being there more annoying. There was a long, anxious pause.
-- Sorry.
-- You're sorry?! -- Ambrose repeated. This was unexpected. Danielle was never the kind of girl to apologize.
-- I'm sorry because I really try, but I can't find it in me to give a rat's ass what you think of me. I mean, you're just a nerdy dude who doesn't have enough spine to
stand up to his stupid bullies, and who left alone would just stand around drooling fantasizing about being a macho superhero saving a lot of defenseless naked virgins.
And this? -- she pointed at the drawing of her on the notebook. He had depicted her in a somewhat standard fantasy costume, which means she had a lot of skin showing. 
In hindsight, that had been a very bad decision. -- This is absolutely disgusting. Please tell me you don't have a thing for me.
Ambrose blushed pink, trying to find words. Did he have a thing for her? Well, who didn't. She did look like a Suicide Girl, even if a very butch one.
-- I... you... uh, but, if you don't like me, why the hell do you talk to me every fucking day?
-- Because you come out from class early every day! -- she spat. -- What am I supposed to do, pretend I didn't know you, and let those stupid bullies have their way with you?!
-- "Have their way with me"? What the heck, it's not like I'm a damsel and they're gonna rape me or something!
-- And besides -- she continued, ignoring his objection -- This time you dragged me into it with your stupid fantasy drawing.
She pushed the notebook into his hands with violence. He had nothing more to say, so they just stood there, waiting in angry silence.
Then he spotted his friends crossing the yard, immersed in some argument that he couldn't make out. He meant to call for them, but Dani was faster.
-- Heey! -- she called with such amicable voice that he could hardly believe it himself that they had been fighting minutes earlier. Was all of this an act? She was so damn fake.
His friends waived and walked over. They were an odd pair, the short brown girl with an afro puff carrying a huge backpack, and the tall, fat, bearded latino
who carried all his books in a shoulder bag.

